Automatic Bicycle Balance Assistance Reduces Probability of Falling at Low Speeds When Subjected to Handlebar Perturbations\\Version 2.dev

### 2024-10-03 main.tex
Use kappa for the gain factor.

\subsection{Balance Assist Control}
%
We use a forward speed \(v\) gain scheduled proportional roll angular rate
feedback controller to stabilize the bicycle. In the speed range tested, the
commanded steer torque \(T^\textrm{m}_\delta\) from the steer motor follows the
control law
%
\begin{align}
  T^\textrm{m}_\delta = -k_{\dot{\phi}}\dot{\phi} = \eta(v_{stable} - v)\dot{\phi}
  \label{eq:implemented-controller}
\end{align}
%
where \(v_{\textrm{stable}} = 4.7~\si{\meter\per\second}\) is approximately the
average stable speed predicted from the open loop bicycle rigid-rider dynamics.
We use the gain factor \(\eta=8\) (low) and \(\eta=10\) (high) to tune the gain
magnitude during the experiments. Scaling the proportional feedback gain
linearly with respect to speed stabilizes the normally unstable weave mode of
the bicycle down to 2.9~\si{\kilo\meter\per\hour} for the riderless bicycle and
4.6~\si{\kilo\meter\per\hour} for the ridden bicycle as shown in
Figure~\ref{fig:eigenvalues}.
%
\begin{figure}
  \centering
  \includegraphics[width=160mm]{figures/balance-assist-eig-vs-speeds.png}
  \caption{Uncontrolled (upper row) and controlled with \(\eta=10\) (lower row)
    root locus of eigenvalue components (real: solid, imaginary: dashed)
    plotted versus speed for the bicycle without the inertial effect of a rigid
    rider (left) and with a rigid rider (right). Vertical dotted and
    dotted-dashed lines indicate the two speeds we perform experiments at. Grey
    shaded region is the linear stable speed range. Geometric and inertial
    parameters for these plots were estimated with the methods presented in
    \citet{Moore2012} and software packages BicycleParameters
    1.1.1~\citep{Moore2024} and Yeadon 1.5.0~\citep{Dembia2015} and are shown
    in Appendix~\ref{sec:physical-parameters}.}
  \label{fig:eigenvalues}
\end{figure}

@@

The participants were divided into two groups. The first group of fifteen
participants performed the protocol at a belt speed of
10~\si{\kph}(2.8~\si{\mps}) with the controller factor set to $g=8$ and two
weeks later the second group of eleven particpants performed the protocol at a
belt speed of 6~\si{\kph} (1.7~\si{\mps}) with the controller factor set to
$g=10$.

@@

We record the order number of each perturbation \(j\), i.e. first, second,
third, \ldots, to measure how many perturbations a rider is subjected to before
the current perturbation. At the initiation of each perturbation we log the
instantaneous steer and roll angles to characterize the configuration of the
bicycle when perturbed. The gain factor setting on the balance assist controller
indicates if the assistance is off \(\eta=0\) or on at two different levels: low
\(\eta=8\) or high \(\eta=10\). A recovery from the perturbation is successful if the
person neither places their foot down onto the treadmill surface nor their
wheel of the bicycle exits the width of the treadmill belt. We record this as a
binary variable \(f\) for ``fall''. All measured variables are reported in
Table~\ref{tab:raw}.
%
\begin{table}
  \centering
  \caption{Raw measurements taken during each trial. ``Fall Outcome'' and
    ``Perturbation Order Number'' are recorded per perturbation instance. The
    remaining measures are time varying during each trial.}
  \begin{tabular}{llll}
    \toprule
    Measure & Variable & Units & Sensor \\
    \midrule
    Balance Assist Gain Factor & \(\eta\) & \si{\newton\second\squared} & NA \\
    Bicycle Speed & \(v\) & \si{\meter\per\second} & wheel encoder \\
    Fall Outcome & \(f\) & boolean & NA \\
    Force \(l\)eft/\(r\)ight,\(f\)ront/\(r\)ear &
    \(F_{lf},F_{rf},F_{lr},F_{rr}\) & \si{\newton} & inline load cell\\
    Perturbation Order Number & \(j\) & integer & NA\\
    Roll Angle & \(\phi\) & \si{\degree} & BN0086 Kalman estimate \\
    Roll Angular Rate & \(\dot{\phi}\) & \si{\degree\per\second} & BN0086 rate gyroscope \\
    Steer Angle & \(\delta\) & \si{\degree} & steer tube encoder \\
    \bottomrule
  \end{tabular}
  \label{tab:raw}
\end{table}

@@

Before fitting the model, we scale each independent variable \(x_{ij}^k\) such
that they have a mean of zero and a standard deviation of one by cluster-mean
centering, as recommended by \citet{Enders2007}, with clusters being an
individual participant. The clusters are chosen as all data from an individual
participant because we are only interested in the association between the state
of the balance assist system and the outcome of the perturbation. We expected
there to be a variation between participants in how well they are able to
resist the perturbation; however, this was not true. Cluster-mean centering
showed there to be no variation between participants. This fact allows us to
utilize a simple single-level logistic regression model, instead of a
multilevel model. This left us with angular impulse, perturbation order,
balance assist state, and roll \& steer angles at the time of perturbation as
independent variables. We also include interaction effects between the balance
assist state and the other four variables. We divide the analysis into two
separate model evaluations, one for the 6~\si{\kph}, \(\eta=10\) trials and one
for the 10~\si{\kph}, \(\eta=8\) trials and we evaluate our hypothesis for each
set of data. Statistics were computed with the lme4 version
1.1~\citep{Bates2015} package in R version 4.1.3~\citep{RCoreTeam2021}.

\section{Results}
%
The coefficient estimates for a single-level logistic regression for the data
from the 6~\si{\kph}, gain factor $g=10$ trials are shown in
Table~\ref{tab:freq-coefs-6}. The angular impulse, perturbation order, and
balance assist state are all statistically significant predictors with angular
impulse having a dominant effect. Larger angular impulse increases the
probability to fall and both enduring more perturbations or having the balance
assist on, decrease the probability to fall. The associated multiplicative
change in odds are shown in Table~\ref{tab:freq-coefs-6}.
%
\begin{table}
  \centering
  \caption{Logistic regression coefficient estimates \(\alpha_k\) at
    6~\si{\kph} and gain factor $g=10$ along with the standard error SE, p-value
    \(p\), multiplicative change in odds \(e^{\alpha_k}\), and the 5\%
    confidence interval bounds.}
  \label{tab:freq-coefs-6}
  \begin{tabular}{lrrrrrr}
    \toprule
    Variable & \(\alpha_k\) & SE & \(p\) & \(e^{\alpha_k}\) & 2.5\% & 97.5\% \\
    \midrule
    Intercept \(\beta\)                           & -0.29 & 0.17 & 0.09 & 0.75 & 0.53 & 1.05 \\
    Angular impulse \(L\)                         & 1.69 & 0.27 & 0.00\(^*\) & 5.40 & 3.18 & 9.16 \\
    Perturbation order \(j\)                      & -0.77 & 0.22 & 0.00\(^*\) & 0.46 & 0.30 & 0.72 \\
    Balance assist state \(s\)                    & -0.64 & 0.27 & 0.02\(^*\) & 0.53 & 0.31 & 0.89 \\
    Roll angle \(\phi_0\)                         & -0.25 & 0.21 & 0.24 & 0.78 & 0.51 & 1.18 \\
    Steer angle \(\delta_0\)                      & -0.14 & 0.21 & 0.51 & 0.87 & 0.58 & 1.32 \\
    Balance assist state $\times$ roll angle         & 0.52 & 0.34 & 0.12 & 1.68 & 0.86 & 3.29 \\
    Balance assist state $\times$ steer angle        & -0.41 & 0.34 & 0.22 & 0.66 & 0.34 & 1.28 \\
    Balance assist state $\times$ angular impulse    & 0.41 & 0.41 & 0.32 & 1.51 & 0.67 & 3.38 \\
    Balance assist state $\times$ perturbation order & -0.53 & 0.34 & 0.12 & 0.59 & 0.30 & 1.15 \\
    \bottomrule
  \end{tabular}
\end{table}

The coefficient estimates for a single-level logistic regression at
10~\si{\kph} with gain factor $g=8$ are shown in Table \ref{tab:freq-coefs-10}. The
angular impulse and perturbation order are statistically significant predictors
with angular impulse being the dominant effect. Larger angular impulse
increases the probability to fall and enduring more perturbations decreases the
probability to fall. Unlike the 6~\si{\kph} trials, the balance assist state is
not a significant predictor but the effect would be a reduction in the
probability to fall if it were. At both speeds, the angular impulse has about
twice the magnitude in effect as the perturbation order.
%
\begin{table}
  \centering
  \caption{Logistic regression coefficient estimates \(\alpha_k\) at
    10~\si{\kph} and gain factor $g=8$ along with the standard error SE, p-value
    \(p\), multiplicative change in odds \(e^{\alpha_k}\), and the 5\%
    confidence interval bounds.}
  \label{tab:freq-coefs-10}
  \begin{tabular}{lrrrrrr}
    \toprule
    Variable & \(\alpha_k\) & SE & \(p\) & \(e^{\alpha_k}\) & 2.5\% & 97.5\% \\
    \midrule
    Intercept                & -0.24 & 0.16 & 0.13 & 0.78 & 0.57 & 1.07 \\
    Angular impulse \(L\)    & 2.39  & 0.29 & 0.00\(^*\) & 10.92 & 6.23 & 19.13 \\
    Perturbation order \(j\) & -1.16 & 0.21 & 0.00\(^*\)  & 0.31 & 0.21 & 0.48 \\
    Balance assist on \(s\)  & -0.44 & 0.24 & 0.07 & 0.64 & 0.40 & 1.03 \\
    Roll angle \(\phi_0\)    & 0.27  & 0.22 & 0.22 & 1.31 & 0.85 & 2.04 \\
    Steer angle \(\delta_0\) & -0.37 & 0.24 & 0.12 & 0.69 & 0.43 & 1.10 \\
    Balance assist state $\times$ roll angle         & -0.61 & 0.34 & 0.08 & 0.54 & 0.28 & 1.07 \\
    Balance assist state $\times$ steer angle        & 0.56  & 0.35 & 0.11 & 1.76 & 0.88 & 3.50 \\
    Balance assist state $\times$ angular impulse    & 0.46  & 0.44 & 0.29 & 1.59 & 0.68 & 3.74 \\
    Balance assist state $\times$ perturbation order & -0.37 & 0.32 & 0.25 & 0.69 & 0.37 & 1.30 \\
    \bottomrule
  \end{tabular}
\end{table}

@@

\appendix
\setcounter{table}{0}
\renewcommand{\thetable}{A.\arabic{table}}
%
\section{Physical Parameters}
\label{sec:physical-parameters}
%
Physical parameters for the balance assist bicycle with and without a rider.
These are found using the measurement approach for geometric and inertial
parameters for a bicycle explained in \citet{Moore2012}. The rider inertial
parameters are derived from the 83.5~\si{\kilogram} rider ``Jason'' available
in BicycleParameters 1.1.1~\citep{Moore2024}. The variable names match the
notation and definitions from the benchmark bicycle model presented in
\citet{Meijaard2007}.
%
\begin{table}[ht]  % have to use "h" so that it stays within the appendix
  \centering
  \caption{Physical parameters of the balance assist bicycle with and without
    the inertia effects of a rigid rider.}
  \begin{tabular}{llrr}
    \toprule
    Variable & Unit & Without Rider & With Rider \\
    \midrule
    \(c\) & \si{\meter} & 0.04 & 0.04 \\
    \(g\) & \si{\meter\per\second\squared} & 9.80665 & 9.80665 \\
    \(I_{Bxx}\) & \si{\kilogram\meter\squared} & 1.12 & 19.7 \\
    \(I_{Bxz}\) & \si{\kilogram\meter\squared} & 0.05 & -3.5 \\
    \(I_{Byy}\) & \si{\kilogram\meter\squared} & 3.16 & 22.7 \\
    \(I_{Bzz}\) & \si{\kilogram\meter\squared} & 2.12 & 5.0 \\
    \(I_{Fxx}\) & \si{\kilogram\meter\squared} & 0.0995 & 0.0995 \\
    \(I_{Fyy}\) & \si{\kilogram\meter\squared} & 0.1902 & 0.1902 \\
    \(I_{Hxx}\) & \si{\kilogram\meter\squared} & 0.298 & 0.298 \\
    \(I_{Hxz}\) & \si{\kilogram\meter\squared} & -0.038 & -0.038 \\
    \(I_{Hyy}\) & \si{\kilogram\meter\squared} & 0.257 & 0.257 \\
    \(I_{Hzz}\) & \si{\kilogram\meter\squared} & 0.057 & 0.057 \\
    \(I_{Rxx}\) & \si{\kilogram\meter\squared} & 0.1023 & 0.1023 \\
    \(I_{Ryy}\) & \si{\kilogram\meter\squared}& 0.1887 & 0.1887 \\
    \(\lambda\) & \si{\radian} & 0.25 & 0.25 \\
    \(m_B\) & \si{\kilogram} & 22.50 & 106.00 \\
    \(m_F\) & \si{\kilogram} & 2.23 & 2.23 \\
    \(m_H\) & \si{\kilogram} & 4.30 & 4.30 \\
    \(m_R\) & \si{\kilogram} & 4.08 & 4.08 \\
    \(r_F\) & \si{\meter} & 0.3523 & 0.3523 \\
    \(r_R\) & \si{\meter} & 0.3489 & 0.3489 \\
    \(w\) & \si{\meter} & 1.113 & 1.113 \\
    \(x_B\) & \si{\meter} & 0.52 & 0.374 \\
    \(x_H\) & \si{\meter} & 0.92 & 0.92 \\
    \(z_B\) & \si{\meter} & -0.52 & -1.009 \\
    \(z_H\) & \si{\meter} & -0.860 & -0.860 \\
    \bottomrule
  \end{tabular}
\end{table}

>>>>

\subsection{Balance Assist Control}
%
We use a forward speed \(v\) gain scheduled proportional roll angular rate
feedback controller to stabilize the bicycle. In the speed range tested, the
commanded steer torque \(T^\textrm{m}_\delta\) from the steer motor follows the
control law
%
\begin{align}
  T^\textrm{m}_\delta = -k_{\dot{\phi}}\dot{\phi} = \kappa(v_{stable} - v)\dot{\phi}
  \label{eq:implemented-controller}
\end{align}
%
where \(v_{\textrm{stable}} = 4.7~\si{\meter\per\second}\) is approximately the
average stable speed predicted from the open loop bicycle rigid-rider dynamics.
We use the gain factor \(\kappa=8\) (low) and \(\kappa=10\) (high) to tune the gain
magnitude during the experiments. Scaling the proportional feedback gain
linearly with respect to speed stabilizes the normally unstable weave mode of
the bicycle down to 2.9~\si{\kilo\meter\per\hour} for the riderless bicycle and
4.6~\si{\kilo\meter\per\hour} for the ridden bicycle as shown in
Figure~\ref{fig:eigenvalues}.
%
\begin{figure}
  \centering
  \includegraphics[width=160mm]{figures/balance-assist-eig-vs-speeds.png}
  \caption{Uncontrolled (upper row) and controlled with \(\kappa=10\) (lower row)
    root locus of eigenvalue components (real: solid, imaginary: dashed)
    plotted versus speed for the bicycle without the inertial effect of a rigid
    rider (left) and with a rigid rider (right). Vertical dotted and
    dotted-dashed lines indicate the two speeds we perform experiments at. Grey
    shaded region is the linear stable speed range. Geometric and inertial
    parameters for these plots were estimated with the methods presented in
    \citet{Moore2012} and software packages
    BicycleParameters~1.1.1~\citep{Moore2024} and
    Yeadon~1.5.0~\citep{Dembia2015} and are shown in
    Appendix~\ref{sec:physical-parameters}.}
  \label{fig:eigenvalues}
\end{figure}

@@

The participants were divided into two groups. The first group of fifteen
participants performed the protocol at a belt speed of
10~\si{\kph}(2.8~\si{\mps}) with the controller factor set to \(\kappa=8\) and two
weeks later the second group of eleven particpants performed the protocol at a
belt speed of 6~\si{\kph} (1.7~\si{\mps}) with the controller factor set to
\(\kappa=10\).

@@

We record the order number of each perturbation \(j\), i.e. first, second,
third, \ldots, to measure how many perturbations a rider is subjected to before
the current perturbation. At the initiation of each perturbation we log the
instantaneous steer and roll angles to characterize the configuration of the
bicycle when perturbed. The gain factor setting on the balance assist controller
indicates if the assistance is off \(\kappa=0\) or on at two different levels: low
\(\kappa=8\) or high \(\kappa=10\). A recovery from the perturbation is successful if the
person neither places their foot down onto the treadmill surface nor their
wheel of the bicycle exits the width of the treadmill belt. We record this as a
binary variable \(f\) for ``fall''. All measured variables are reported in
Table~\ref{tab:raw}.
%
\begin{table}
  \centering
  \caption{Raw measurements taken during each trial. ``Fall Outcome'' and
    ``Perturbation Order Number'' are recorded per perturbation instance. The
    remaining measures are time varying during each trial.}
  \begin{tabular}{llll}
    \toprule
    Measure & Variable & Units & Sensor \\
    \midrule
    Balance Assist Gain Factor & \(\kappa\) & \si{\newton\second\squared} & NA \\
    Bicycle Speed & \(v\) & \si{\meter\per\second} & wheel encoder \\
    Fall Outcome & \(f\) & boolean & NA \\
    Force \(l\)eft/\(r\)ight,\(f\)ront/\(r\)ear &
    \(F_{lf},F_{rf},F_{lr},F_{rr}\) & \si{\newton} & inline load cell\\
    Perturbation Order Number & \(j\) & integer & NA\\
    Roll Angle & \(\phi\) & \si{\degree} & BN0086 Kalman estimate \\
    Roll Angular Rate & \(\dot{\phi}\) & \si{\degree\per\second} & BN0086 rate gyroscope \\
    Steer Angle & \(\delta\) & \si{\degree} & steer tube encoder \\
    \bottomrule
  \end{tabular}
  \label{tab:raw}
\end{table}

@@

Before fitting the model, we scale each independent variable \(x_{ij}^k\) such
that they have a mean of zero and a standard deviation of one by cluster-mean
centering, as recommended by \citet{Enders2007}, with clusters being an
individual participant. The clusters are chosen as all data from an individual
participant because we are only interested in the association between the state
of the balance assist system and the outcome of the perturbation. We expected
there to be a variation between participants in how well they are able to
resist the perturbation; however, this was not true. Cluster-mean centering
showed there to be no variation between participants. This fact allows us to
utilize a simple single-level logistic regression model, instead of a
multilevel model. This left us with angular impulse, perturbation order,
balance assist state, and roll \& steer angles at the time of perturbation as
independent variables. We also include interaction effects between the balance
assist state and the other four variables. We divide the analysis into two
separate model evaluations, one for the 6~\si{\kph}, \(\kappa=10\) trials and one
for the 10~\si{\kph}, \(\kappa=8\) trials and we evaluate our hypothesis for each
set of data. Statistics were computed with the lme4 version
1.1~\citep{Bates2015} package in R version 4.1.3~\citep{RCoreTeam2021}.

\section{Results}
%
The coefficient estimates for a single-level logistic regression for the data
from the 6~\si{\kph}, gain factor \(\kappa=10\) trials are shown in
Table~\ref{tab:freq-coefs-6}. The angular impulse, perturbation order, and
balance assist state are all statistically significant predictors with angular
impulse having a dominant effect. Larger angular impulse increases the
probability to fall and both enduring more perturbations or having the balance
assist on, decrease the probability to fall. The associated multiplicative
change in odds are shown in Table~\ref{tab:freq-coefs-6}.
%
\begin{table}
  \centering
  \caption{Logistic regression coefficient estimates \(\alpha_k\) at
    6~\si{\kph} and gain factor \(\kappa=10\) along with the standard error SE, p-value
    \(p\), multiplicative change in odds \(e^{\alpha_k}\), and the 5\%
    confidence interval bounds.}
  \label{tab:freq-coefs-6}
  \begin{tabular}{lrrrrrr}
    \toprule
    Variable & \(\alpha_k\) & SE & \(p\) & \(e^{\alpha_k}\) & 2.5\% & 97.5\% \\
    \midrule
    Intercept \(\beta\)                           & -0.29 & 0.17 & 0.09 & 0.75 & 0.53 & 1.05 \\
    Angular impulse \(L\)                         & 1.69 & 0.27 & 0.00\(^*\) & 5.40 & 3.18 & 9.16 \\
    Perturbation order \(j\)                      & -0.77 & 0.22 & 0.00\(^*\) & 0.46 & 0.30 & 0.72 \\
    Balance assist state \(s\)                    & -0.64 & 0.27 & 0.02\(^*\) & 0.53 & 0.31 & 0.89 \\
    Roll angle \(\phi_0\)                         & -0.25 & 0.21 & 0.24 & 0.78 & 0.51 & 1.18 \\
    Steer angle \(\delta_0\)                      & -0.14 & 0.21 & 0.51 & 0.87 & 0.58 & 1.32 \\
    Balance assist state $\times$ roll angle         & 0.52 & 0.34 & 0.12 & 1.68 & 0.86 & 3.29 \\
    Balance assist state $\times$ steer angle        & -0.41 & 0.34 & 0.22 & 0.66 & 0.34 & 1.28 \\
    Balance assist state $\times$ angular impulse    & 0.41 & 0.41 & 0.32 & 1.51 & 0.67 & 3.38 \\
    Balance assist state $\times$ perturbation order & -0.53 & 0.34 & 0.12 & 0.59 & 0.30 & 1.15 \\
    \bottomrule
  \end{tabular}
\end{table}

The coefficient estimates for a single-level logistic regression at
10~\si{\kph} with gain factor \(\kappa=8\) are shown in Table \ref{tab:freq-coefs-10}. The
angular impulse and perturbation order are statistically significant predictors
with angular impulse being the dominant effect. Larger angular impulse
increases the probability to fall and enduring more perturbations decreases the
probability to fall. Unlike the 6~\si{\kph} trials, the balance assist state is
not a significant predictor but the effect would be a reduction in the
probability to fall if it were. At both speeds, the angular impulse has about
twice the magnitude in effect as the perturbation order.
%
\begin{table}
  \centering
  \caption{Logistic regression coefficient estimates \(\alpha_k\) at
    10~\si{\kph} and gain factor \(\kappa=8\) along with the standard error SE, p-value
    \(p\), multiplicative change in odds \(e^{\alpha_k}\), and the 5\%
    confidence interval bounds.}
  \label{tab:freq-coefs-10}
  \begin{tabular}{lrrrrrr}
    \toprule
    Variable & \(\alpha_k\) & SE & \(p\) & \(e^{\alpha_k}\) & 2.5\% & 97.5\% \\
    \midrule
    Intercept                & -0.24 & 0.16 & 0.13 & 0.78 & 0.57 & 1.07 \\
    Angular impulse \(L\)    & 2.39  & 0.29 & 0.00\(^*\) & 10.92 & 6.23 & 19.13 \\
    Perturbation order \(j\) & -1.16 & 0.21 & 0.00\(^*\)  & 0.31 & 0.21 & 0.48 \\
    Balance assist on \(s\)  & -0.44 & 0.24 & 0.07 & 0.64 & 0.40 & 1.03 \\
    Roll angle \(\phi_0\)    & 0.27  & 0.22 & 0.22 & 1.31 & 0.85 & 2.04 \\
    Steer angle \(\delta_0\) & -0.37 & 0.24 & 0.12 & 0.69 & 0.43 & 1.10 \\
    Balance assist state $\times$ roll angle         & -0.61 & 0.34 & 0.08 & 0.54 & 0.28 & 1.07 \\
    Balance assist state $\times$ steer angle        & 0.56  & 0.35 & 0.11 & 1.76 & 0.88 & 3.50 \\
    Balance assist state $\times$ angular impulse    & 0.46  & 0.44 & 0.29 & 1.59 & 0.68 & 3.74 \\
    Balance assist state $\times$ perturbation order & -0.37 & 0.32 & 0.25 & 0.69 & 0.37 & 1.30 \\
    \bottomrule
  \end{tabular}
\end{table}

@@

\appendix
\setcounter{table}{0}
\renewcommand{\thetable}{A.\arabic{table}}
%
\section{Physical Parameters}
\label{sec:physical-parameters}
%
Physical parameters for the balance assist bicycle with and without a rider.
These are found using the measurement approach for geometric and inertial
parameters for a bicycle explained in \citet{Moore2012}. The rider inertial
parameters are derived from the 83.5~\si{\kilogram} rider ``Jason'' available
in BicycleParameters~1.1.1~\citep{Moore2024}. The variable names match the
notation and definitions from the benchmark bicycle model presented in
\citet{Meijaard2007}.
%
\begin{table}[ht]  % have to use "h" so that it stays within the appendix
  \centering
  \caption{Physical parameters of the balance assist bicycle with and without
    the inertia effects of a rigid rider.}
  \begin{tabular}{llrr}
    \toprule
    Variable & Unit & Without Rider & With Rider \\
    \midrule
    \(c\) & \si{\meter} & 0.04 & 0.04 \\
    \(g\) & \si{\meter\per\second\squared} & 9.80665 & 9.80665 \\
    \(I_{Bxx}\) & \si{\kilogram\meter\squared} & 1.12 & 19.7 \\
    \(I_{Bxz}\) & \si{\kilogram\meter\squared} & 0.05 & -3.5 \\
    \(I_{Byy}\) & \si{\kilogram\meter\squared} & 3.16 & 22.7 \\
    \(I_{Bzz}\) & \si{\kilogram\meter\squared} & 2.12 & 5.0 \\
    \(I_{Fxx}\) & \si{\kilogram\meter\squared} & 0.0995 & 0.0995 \\
    \(I_{Fyy}\) & \si{\kilogram\meter\squared} & 0.1902 & 0.1902 \\
    \(I_{Hxx}\) & \si{\kilogram\meter\squared} & 0.298 & 0.298 \\
    \(I_{Hxz}\) & \si{\kilogram\meter\squared} & -0.038 & -0.038 \\
    \(I_{Hyy}\) & \si{\kilogram\meter\squared} & 0.257 & 0.257 \\
    \(I_{Hzz}\) & \si{\kilogram\meter\squared} & 0.057 & 0.057 \\
    \(I_{Rxx}\) & \si{\kilogram\meter\squared} & 0.1023 & 0.1023 \\
    \(I_{Ryy}\) & \si{\kilogram\meter\squared}& 0.1887 & 0.1887 \\
    \(\lambda\) & \si{\radian} & 0.25 & 0.25 \\
    \(m_B\) & \si{\kilogram} & 22.50 & 106.00 \\
    \(m_F\) & \si{\kilogram} & 2.23 & 2.23 \\
    \(m_H\) & \si{\kilogram} & 4.30 & 4.30 \\
    \(m_R\) & \si{\kilogram} & 4.08 & 4.08 \\
    \(r_F\) & \si{\meter} & 0.3523 & 0.3523 \\
    \(r_R\) & \si{\meter} & 0.3489 & 0.3489 \\
    \(w\) & \si{\meter} & 1.113 & 1.113 \\
    \(x_B\) & \si{\meter} & 0.52 & 0.374 \\
    \(x_H\) & \si{\meter} & 0.92 & 0.92 \\
    \(z_B\) & \si{\meter} & -0.52 & -1.009 \\
    \(z_H\) & \si{\meter} & -0.860 & -0.860 \\
    \bottomrule
  \end{tabular}
\end{table}
